Supplementary Information: Tropical tree drought sensitivity is jointly shaped by drought characteristics, species adaptations, and individual microenvironments

### 2025-04-16 doc/supplementary_information.Rmd
@teixeirak - knit version of today's changes
remove neg growth from SI #28
updating SI
update SI with better cond dep figs
updated SI figures, captions from 1-6

![Figure S1: Raw climate data timeseries](display/climvars_fullseries.png)

![Figure S2: Climate anomalies across the whole timeseries](display/climvars_anomalies_fullseries.png)
\newpage

@@

## Species traits and correlations

![](display/Fig_SI_species_sensitivities.png)

![](display/Fig_SI_sensitivity_cor_dec.png)

![](display/Fig_trait_intercept_plot.png)

@@

## Individual growth and correlations

- Negative growth proportions across the years

![](display/sens_corr.png)

@@

![](display/explore/twi.png)

![](display/explore/dbh_cii.png)

@@

## Growth occurrence models

To add: zero growth models

>>>>

![*Figure S1:* Raw climate data timeseries from 2009 to 2020 from the Forest Fire Research Station near HKK. Measurements represent daily rolling means over a 30-day time window for precipitation, max temperature and VPD and rolling sum for number of dry days.](display/climvars_fullseries.png)

![*Figure S2:* Climate anomalies for all variables from 2009 to 2020from the Forest Fire Research Station near HKK. Values represent number of standard deviations from the long-term mean for daily rolling mean values.](display/climvars_anomalies_fullseries.png)

@@

## Growth timeseries and anomalies

![*Figure S3:* Growth anomalies across the timeseries. Growth anomalies for each year calculated as the number of standard deviations in growth each year from mean growth across all years and summarised for plot and species.](display/growth_anom_fullseries.png)

<!-- ![Fig S4: Proportion of negative growth increments](display/neg_incs.png) -->

@@

## Drought year growth of species and individuals

![*Figure S4:* Species sensitivities in drought years 2010 and 2015. Boxplots represent 25th, 50th (median) and 75th percentile of sensitivity for each species in each year and whiskers represent 95% CIs. All individual sensitivities represented by jittered points.](display/Fig_SI_species_sensitivities.png)

![*Figure S5:* Correlations of species sensitivities across the two years. Panel a shows correlation of species median sensitivities in the two years and Pearson's correlation coefficient. Colour gradient represents deciduousness scale and dotted line is the 1:1 line. Panel b shows difference in magnitude of species median sensitivites among the two years](display/Fig_SI_sensitivity_cor_dec.png)

<!-- ![](display/Fig_trait_intercept_plot.png) -->

![*Figure S6:* Correlation of individual sensitivities across the two years along with Pearson's correlation coefficient and the 1:1 line.](display/sens_corr.png)

@@

Map of trees

![Fig S7:](display/dendro_tree_map.png)

![Fig S8:](display/explore/twi.png)

![Fig S9: ](display/explore/dbh_cii.png)

## Conditional dependencies

![Fig S10:](display/explore/cond_dep_alltrees.png)

![Fig S11: ](display/explore/cond_dep_dbh_twi.png)

![Fig S12:](display/explore/cond_dep_cii_twi.png)

@@

<!-- ## Growth occurrence models

To add: zero growth models -->
